Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-02-14 3dpas_intro.tex
ongoing work in the conclusion section.

This section brings together some key observations
from the applications and infrastructure
analysis carried out in this paper.
%as take away messages. 
Section~\ref{sec:discussion}
provides a discussion of dynamic and distributed characteristics of
data associated with the applications we analyze in this work,
attempting to infer more general characteristics that %can be applied
may apply
to other similar applications.  We also suggest two metrics that may
suggest two metrics that may
be associated with such applications, primarily as a basis to compare
how compute and data processing (in terms of their number and
distribution) may be used to find common features between them. Such
feature analysis is useful, we believe, for two main reasons: (i) to
identify similarities between the applications covered in
\S\ref{sec:scenarios} with others that are in the design phase or
under development, so that common requirements can be identified; and
(ii) to identify gaps in current software tools and programming
systems that such applications use, thereby leading to the
development of new tools and systems. As our application and
infrastructure coverage is, by necessity, limited, identifying common
features also enables the lessons learned to be generalized and
applied more widely. We subsequently discuss a set of architectures
for D3 science, and pose some questions we believe are pertinent as
the community begins considering the next-generation
architectures for D3 applications. In
\S\ref{sec:conclusion} we conclude by providing a number of
observations to inform applications and
cyberinfrastructure developers, based on common trends found in our study.

@@

In this section we attempt to summarize four key themes from previous
sections: (i) the source and nature of dynamic data that we observe in
the application surveyed in \S\ref{sec:scenarios}; (ii) the types of
data distribution that we observe in such applications; (iii) the
general characteristics that can be associated with D3 science
applications; (iv) the characteristics of a computational
infrastructure that may be most suited for D3 science
applications. Whereas (i) and (ii) are primarily observations that we
can make on existing applications that we have discussed in
\S\ref{sec:scenarios}, (iii) and (iv) attempt to synthesize general
trends that can be applied to other applications we have not
considered. 
%\katznote{should this be split into two subsections then? Perhaps Observations \& Trends?}

>>>>

%as take away messages.

This section brings together some key observations from the applications and
infrastructure analysis carried out in this paper.  Section~\ref{sec:discussion}
provides a discussion of dynamic and distributed characteristics of data
associated with the applications we analyze in this work, attempting to infer
more general characteristics that %can be applied
may apply to other similar applications.  We also suggest two metrics that may
suggest two metrics that may be associated with such applications, primarily as
a basis to compare how compute and data processing (in terms of their number and
distribution) may be used to find common features between them. Such feature
analysis is useful, we believe, for two main reasons: (i) to identify
similarities between the applications covered in \S\ref{sec:scenarios} with
others that are in the design phase or under development, so that common
requirements can be identified; and (ii) to identify gaps in current software
tools and programming systems that such applications use, thereby leading to the
development of new tools and systems. As our application and infrastructure
coverage is, by necessity, limited, identifying common features also enables the
lessons learned to be generalized and applied more widely. We subsequently
discuss a set of architectures for D3 science, and pose some questions we
believe are pertinent as the community begins considering the next-generation
architectures for D3 applications. In \S\ref{sec:conclusion} we conclude by
providing a number of observations to inform applications and
cyberinfrastructure developers, based on common trends found in our study.

@@

We summarize four key themes from previous sections: (i) the source and nature
of dynamic data observed in the applications surveyed in \S\ref{sec:scenarios};
(ii) the types of data distribution observed in such applications; (iii) the
general characteristics that can be associated with D3 science applications;
(iv) the characteristics of a computational infrastructure most suited for D3
science applications.  Whereas (i) and (ii) are observations that can be made on
existing applications discussed in \S\ref{sec:scenarios}, (iii) and (iv) attempt
to synthesize general trends that can be applied to applications we have not
considered.

%\katznote{should this be split into two subsections then? Perhaps Observations \& Trends?}
